HPC--101\\Onboarding

### 2016-06-09 hpc_101/paper.tex
changed text regarding scheduler priority setting
Addition of the job array image

\subsection{SLURM}
\begin{frame}
\frametitle{SLURM}
\begin{block}{How are jobs scheduled?}
User submitted jobs are assigned a priority using a fairshare algorithm.\\
Factors such as the following are all used to assign a priority to a given job: 
\begin{itemize}
\item Runtime
\item Resource usage request
\item Age of job
\item Amount of core hours a user has used in recent history
\end{itemize}

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem=11000 \#\# max amount of memory per node you require
\#SBATCH \ddash{}error=buzz-\%A\_\%a.err \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#SBATCH \ddash{}output=buzz-\%A\_\%a.out \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

./worker\_bee -i input\_\$\{SLURM_ARRAY_TASK_ID\}.flower -o output\_\$\{SLURM_ARRAY_TASK_ID\}.honey
\end{semiverbatim}
\end{frame}

@@

\subsection{Executing and Monitoring Batch Jobs}
\begin{frame}[fragile]
\frametitle{SLURM sbatch -- Executing \& Monitoring Jobs}\footnotesize
To execute a submission script you use the \textbf{\texttt{sbatch}} command
\begin{block}{Example -- Non Job Array}
\begin{semiverbatim}\tiny
[login lus]\$ sinfo
PARTITION     AVAIL  TIMELIMIT  NODES  STATE NODELIST
community.q   up     3-00:00:00 2      idle  compute-[0001-0002]
[login lus]\$ sbatch hello_world.slurm
sbatch: Submitted batch job 469
[login lus]\$ squeue
JOBID PARTITION    NAME     USER    ST TIME  NODES  NODELIST(REASON)
469   community.q  example  user99  R  00:01 1      compute-0001
\end{semiverbatim}
\end{block}
\begin{block}{Example -- Job Array}
\begin{semiverbatim}\tiny
[login lus]\$ sinfo
PARTITION     AVAIL  TIMELIMIT  NODES  STATE NODELIST
community.q   up     3-00:00:00 2      idle  compute-[0001-0002]
[login lus]\$ sbatch {\ddash}array=0-2 job_array.slurm
sbatch: Submitted batch job 470
[login lus]\$ squeue
JOBID     PARTITION    NAME     USER    ST   TIME    NODES  NODELIST(REASON)
470[0-2]  community.q  example  user99  PD   00:00   1      (resource)
470_0     community.q  example  user99  R    00:01   1      compute-0001
470_1     community.q  example  user99  R    00:05   1      compute-0002
\end{semiverbatim}
\end{block}

>>>>

\subsection{SLURM}
\begin{frame}
\frametitle{SLURM}
\begin{block}{How are jobs scheduled?}
User submitted jobs are assigned a priority using a fairshare algorithm.\\
Factors such as the following are all used to assign a priority to a given job: 
\begin{itemize}
\item Runtime
\item Amount of resources requested
\item Age of job
\item Amount of core hours a user has used in recent history
\end{itemize}

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem=11000 \#\# max amount of memory per node you require
\#SBATCH \ddash{}error=myprog-\%A\_\%a.err \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#SBATCH \ddash{}output=myprog-\%A\_\%a.out \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

./worker\_bee -i input\_\$\{SLURM_ARRAY_TASK_ID\}.dat -o output\_\$\{SLURM_ARRAY_TASK_ID\}
\end{semiverbatim}
\end{frame}

@@

\subsection{Executing and Monitoring Batch Jobs}
\begin{frame}[fragile]
\frametitle{SLURM sbatch -- Executing \& Monitoring Jobs}\footnotesize
To execute a submission script you use the \textbf{\texttt{sbatch}} command
\begin{block}{Example -- Non Job Array}
\begin{semiverbatim}\tiny
[login lus]\$ sinfo
PARTITION     AVAIL  TIMELIMIT  NODES  STATE NODELIST
community.q   up     3-00:00:00 2      idle  compute-[0001-0002]
[login lus]\$ sbatch hello_world.slurm
sbatch: Submitted batch job 469
[login lus]\$ squeue
JOBID PARTITION    NAME     USER    ST TIME  NODES  NODELIST(REASON)
469   community.q  example  user99  R  00:01 1      compute-0001
\end{semiverbatim}
\end{block}
\begin{block}{Example -- Job Array}
\begin{semiverbatim}\tiny
[login lus]\$ sinfo
PARTITION     AVAIL  TIMELIMIT  NODES  STATE NODELIST
community.q   up     3-00:00:00 2      idle  compute-[0001-0002]
[login lus]\$ sbatch {\ddash}array=1-30 job_array.slurm
sbatch: Submitted batch job 470
[login lus]\$ squeue
JOBID      PARTITION    NAME     USER    ST   TIME    NODES  NODELIST(REASON)
470[1-30]  community.q  example  user99  PD   00:00   1      (resource)
470_1      community.q  example  user99  R    00:01   1      compute-0001
470_2      community.q  example  user99  R    00:05   1      compute-0002
\end{semiverbatim}
\end{block}

\begin{frame}
  \frametitle{Slurm Job Array}
  \includegraphics[width=1\textwidth]{images/job_array}
